### 2016-04-14 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some work on boxcar + FIX BUG

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. 
As shown in \citet{Pintelon2012} and \citet{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}

@@

\begin{assumption}
The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\cite{Schoukens2009LPM}.
\end{assumption}

@@

\paragraph{Formulation of the Linear LS LPM}
The \gls{LPM} is formulated as a nonparametric local linear \gls{LS} estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
\citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.
The formulation in this section is a summary for a \gls{SISO} system.

The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
\begin{equation}\label{lpm1spectra}
Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
\end{equation}
where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.

The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
\begin{align}\label{lpmGTaylorS}
G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
\bigO{\left(\frac{r}{N}\right)^{R+1}},
\\
\label{lpmTTaylorS}
T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
\bigO{  \left(\frac{r}{N}\right)^{R+1}  }
,
\\
\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
\end{align}

The choice of the tunable parameters $n$ and $R$ is discussed later on.

Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
\begin{equation}\label{lpmGTMatrix}
Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
\end{equation}
where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
\begin{align}
K(k,r) = &\left[
\begin{matrix}
U_0(k+r) & U_0(k+r)r & \dots
\end{matrix}
\right.
\\
&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
\end{align}

Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
\begin{equation}\label{lpmGTMatrixStack}
Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
\end{equation}
where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
\begin{align}\label{eq:LSsolutionLPM}
\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
\end{align}

The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$. The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{Schoukens2009LPM}.

The values $R = 2$, and $n=R+1=3$ will be used in the \gls{LPM}.

When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
\begin{align}
G_0(\Omega_{k+r})
  &\approx 
  G_0(\Omega_k)+g_1r+g_2r^2
  \label{eq:lpm:expansionG:quadratic}
\\
  T(\Omega_{k+r})
    &\approx 
    T(\Omega_k)+t_1r+t_2r^2
    \label{eq:lpm:expansionT:quadratic}
\end{align}
with ($r\in\mathbb{W}_3$) and the vector of parameters:
\begin{equation}\label{lpmThetaEst}
\theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
\end{equation}
The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
\begin{equation}
\hat{G}_{\LPM}(\Omega_k) = \hat\theta_1(k)
\end{equation}

@@

>>>>

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. 
As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}

@@

\begin{assumption}
The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\citep{Schoukens2009LPM}.
\end{assumption}

@@

%TODO: re-use into LPM/LRM sections
% \paragraph{Formulation of the Linear LS LPM}
% The \gls{LPM} is formulated as a nonparametric local linear \gls{LS} estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
% \citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.
% The formulation in this section is a summary for a \gls{SISO} system.

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.

% The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
% \begin{align}\label{lpmGTaylorS}
% G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
% \bigO{\left(\frac{r}{N}\right)^{R+1}},
% \\
% \label{lpmTTaylorS}
% T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
% \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
% ,
% \\
% \text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
% \end{align}

% The choice of the tunable parameters $n$ and $R$ is discussed later on.

% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
% \begin{equation}\label{lpmGTMatrix}
% Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
% \end{equation}
% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
% \begin{align}
% K(k,r) = &\left[
% \begin{matrix}
% U_0(k+r) & U_0(k+r)r & \dots
% \end{matrix}
% \right.
% \\
% &\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
% \end{align}

% Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
% \begin{equation}\label{lpmGTMatrixStack}
% Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
% \end{equation}
% where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
% The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
% \begin{align}\label{eq:LSsolutionLPM}
% \hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
% \end{align}

% The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$. The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{Schoukens2009LPM}.

% The values $R = 2$, and $n=R+1=3$ will be used in the \gls{LPM}.
In this section, the $\lpm{3,2,2}$ is used.

% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
% \begin{align}
% G_0(\Omega_{k+r})
%   &\approx 
%   G_0(\Omega_k)+g_1r+g_2r^2
%   \label{eq:lpm:expansionG:quadratic}
% \\
%   T(\Omega_{k+r})
%     &\approx 
%     T(\Omega_k)+t_1r+t_2r^2
%     \label{eq:lpm:expansionT:quadratic}
% \end{align}
% with ($r\in\mathbb{W}_3$) and the vector of parameters:
% \begin{equation}\label{lpmThetaEst}
% \theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
% \end{equation}
% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
% \begin{equation}
% \hat{G}_{\LPM}(\Omega_k) = \hat\theta_1(k)
% \end{equation}

@@

\paragraph{Alternative system}
%% BEGIN BOXCAR
\TODO{write about boxcar average, add reference}
\begin{align}
  y(t) = \sum_{i=1}^{\Nbc} \Nbc^{-1} u(t-i)
\end{align}

\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/expFitBoxAverager.tikz}
         \caption{Exponential fit of the impulse response of a boxcar averager.}
         \label{fig:nparam:trunc:boxcar:impresp}
\end{figure}

\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/pdfs-rmse-boxcar.tikz}
         \caption[RMS error of the FRF versus truncation time (boxcar)]{RMSE of a boxcar averager as a function of the truncation time $\truncTime$.
         Empirical histograms of $\truncTime$ as determined using both the $F$-test and exponential fitting are shown.
         For this system, the $F$-test based method is clearly superior.
         The exponential fitting method is not effective in most cases.}
         \label{fig:nparam:trunc:boxcar:trunctime}
\end{figure}
%% END BOXCAR
